Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics

### 2023-03-21 paper/paper.Rmd
figs revised and order of factor levels

```{r pdetection_group}
# Tidy for analysis
d <- d %>% 
  separate(image_name, c("nothing", "trend", "location", "type", "extra"), remove = FALSE) %>%
  select(-nothing, -extra) %>%
  mutate(location = as.numeric(location), 
    # detect measures the accuracy of the choice
         detect = ifelse(location == choice, 1, 0)) %>% 
  mutate(trend = case_when(
    trend == "nwse" ~ "NW-SE",
    trend == "cities" ~ "All Cities",
    trend == "three" ~ "Three Cities")) %>% 
  mutate(trend = fct_relevel(trend, "NW-SE","Three Cities","All Cities")) %>% 
  mutate(type = case_when(
    type == "hex" ~"Hex.",
    TRUE~"Choro.")) %>% 
    mutate(detect_f = factor(detect, levels = c(0,1), labels = c("Detected? No", "Detected? Yes")))

@@

invthm <- theme_map() + 
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA), 
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.key = element_rect(fill = "transparent", colour = NA),
    text = element_text(colour = "white"),
    axis.text = element_text(colour = "white")
  )

>>>>

```{r pdetection_group}
# Tidy for analysis
d <- d %>% 
  separate(image_name, c("nothing", "trend", "location", "type", "extra"), remove = FALSE) %>%
  select(-nothing, -extra) %>%
  mutate(location = as.numeric(location), 
    # detect measures the accuracy of the choice
         detect = ifelse(location == choice, 1, 0)) %>% 
  mutate(trend = case_when(
    trend == "nwse" ~ "NW-SE",
    trend == "cities" ~ "All Cities",
    trend == "three" ~ "Three Cities")) %>% 
  mutate(trend = fct_relevel(trend,"All Cities","Three Cities", "NW-SE")) %>% 
  mutate(type = case_when(
    type == "hex" ~"Hex.",
    TRUE~"Choro.")) %>% 
    mutate(detect_f = factor(detect, levels = c(0,1), labels = c("Detected? No", "Detected? Yes")))

@@

invthm <- theme_map() + 
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA), 
    plot.background = element_rect(fill = "black", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.key = element_rect(fill = "transparent", colour = NA),
    text = element_text(colour = "white"),
    axis.text = element_blank()
  )

### 2023-03-21 paper/paper.tex
figs revised and order of factor levels

\caption{\label{tab:detect-glmer1}The model output for the generalised linear mixed effect model for detection rate. This model considers the type of display, the trend model hidden in the data plot, and accounts for contributor performance.}
\centering
\begin{tabular}[t]{rrlrr}
\toprule
Term & Est. & Sig. & Std. Error & P val\\
\midrule
Intercept & 0.07 & $^{ }$ & 0.16 & 0.67\\
Hex. & 0.46 & $^{*}$ & 0.22 & 0.04\\
\addlinespace
Three Cities & -3.41 & $^{***}$ & 0.42 & 0.00\\
All Cities & -1.34 & $^{***}$ & 0.24 & 0.00\\
\addlinespace
Hex:Three Cities & 2.44 & $^{***}$ & 0.47 & 0.00\\
Hex:All Cities & 1.16 & $^{***}$ & 0.33 & 0.00\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:reason}The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps. The facets show whether or not the choice was correct.}
\centering
\begin{tabular}[t]{llll}
\toprule
Trend & Detected & Choro. & Hex.\\
\midrule
 & No & trend & clusters\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash NW-SE} & Yes & trend & clusters\\
\cmidrule{1-4}
 & No & trend & clusters\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash Three Cities} & Yes & consistent & clusters\\
\cmidrule{1-4}
 & No & trend & clusters\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash All Cities} & Yes & clusters, consistent & clusters\\
\bottomrule
\end{tabular}
\end{table}

@@

\leavevmode\vadjust pre{\hypertarget{ref-atlas}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Cancer Council Queensland {Australian Cancer Atlas (https://atlas.cancer.org.au)}. }

@@

\leavevmode\vadjust pre{\hypertarget{ref-BCM}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Skowronnek A (2016) {Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata}. In: {Infovis Reading Group WS 2015/16}. \href{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}{https://alsino.io/static/papers/BeyondChoropleths\_AlsinoSkowronnek.pdf. }}

@@

\leavevmode\vadjust pre{\hypertarget{ref-ACTUC}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Dorling D (2011) \href{https://doi.org/10.1002/9780470979587.ch33}{{Area Cartograms: Their Use and Creation}}. In: Concepts and techniques in modern geography (CATMOG). pp 252--260}

@@

\leavevmode\vadjust pre{\hypertarget{ref-review}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{(2019) Cancer applications of choropleth maps, and the potential of cartograms and alternative map displays. Manuscript submitted for publication. }

\leavevmode\vadjust pre{\hypertarget{ref-BCHLLSW09}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics. Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383}

@@

\leavevmode\vadjust pre{\hypertarget{ref-abs2016}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{(2018) \href{\%7Bhttps://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)\%7D}{{Australian Statistical Geography Standard (ASGS)}}. Australian Bureau of Statistics }

@@

\leavevmode\vadjust pre{\hypertarget{ref-figeight}{}}%
\CSLLeftMargin{22. }%
\CSLRightInline{(2019) \href{https://www.figure-eight.com/}{The essential high-quality data annotation platform}. Figure Eight }

>>>>

\caption{\label{tab:detect-glmer1}The model output for the generalised linear mixed effect model for detection rate. This model considers the type of display, the trend model hidden in the data plot, and accounts for contributor performance.}
\centering
\begin{tabular}[t]{rrlrr}
\toprule
Term & Est. & Sig. & Std. Error & P val\\
\midrule
Intercept & -1.27 & $^{***}$ & 0.19 & 0.00\\
Hex. & 1.63 & $^{***}$ & 0.24 & 0.00\\
\addlinespace
Three Cities & -2.07 & $^{***}$ & 0.43 & 0.00\\
All Cities & 1.34 & $^{***}$ & 0.24 & 0.00\\
\addlinespace
Hex:Three Cities & 1.28 & $^{**}$ & 0.48 & 0.01\\
Hex:All Cities & -1.16 & $^{***}$ & 0.33 & 0.00\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:reason}The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps. The facets show whether or not the choice was correct.}
\centering
\begin{tabular}[t]{llll}
\toprule
Trend & Detected & Choro. & Hex.\\
\midrule
 & No & trend & clusters\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash All Cities} & Yes & clusters, consistent & clusters\\
\cmidrule{1-4}
 & No & trend & clusters\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash Three Cities} & Yes & consistent & clusters\\
\cmidrule{1-4}
 & No & trend & clusters\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash NW-SE} & Yes & trend & clusters\\
\bottomrule
\end{tabular}
\end{table}

@@

\leavevmode\vadjust pre{\hypertarget{ref-atlas}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Cancer Council Queensland {Australian Cancer Atlas}, publisher = {Queensland University of Technology, Cooperative Research Centre for Spatial Information}, issue = {Version 09}, url={https://atlas.cancer.org.au}, year = {2018}, accessed = {Jan 12 2020}. }

@@

\leavevmode\vadjust pre{\hypertarget{ref-BCM}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Skowronnek A (2016) \href{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}{{Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata}}. {Infovis Reading Group WS 2015/16} }

@@

\leavevmode\vadjust pre{\hypertarget{ref-ACTUC}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Dorling D (2011) \href{https://doi.org/10.1002/9780470979587.ch33}{{Area Cartograms: Their Use and Creation}}. In: Concepts and techniques in modern geography (CATMOG). University of East Anglia: Environmental Publications, pp 252--260}

@@

\leavevmode\vadjust pre{\hypertarget{ref-review}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{Kobakian S, Cook D, Roberts J (2020) \href{https://ace.amegroups.com/article/view/6040}{Mapping cancer: The potential of cartograms and alternative map displays}. Annals of Cancer Epidemiology 4:}

\leavevmode\vadjust pre{\hypertarget{ref-BCHLLSW09}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) \href{https://doi.org/10.1098/rsta.2009.0120}{Statistical inference for exploratory data analysis and model diagnostics}. Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383}

@@

\leavevmode\vadjust pre{\hypertarget{ref-abs2016}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{Australian Bureau of Statistics (2018) \href{https://www.abs.gov.au/statistics/statistical-geography/australian-statistical-geography-standard-asgs}{{Australian Statistical Geography Standard (ASGS)}}. }

@@

\leavevmode\vadjust pre{\hypertarget{ref-figeight}{}}%
\CSLLeftMargin{22. }%
\CSLRightInline{Figure Eight Inc (2019) \href{https://www.figure-eight.com/}{The essential high-quality data annotation platform}. }
